Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ Fcross-correlations

### 2019-09-14 notes/paper/paper.tex
added parameter talk

\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations}
\author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK\\
                      $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, United Kingdom
                      }

@@

    \subsubsection{Galaxies and the halo occupation distribution}\label{sssec:theory.hm.hod}
      To model the galaxy overdensity, $\Delta_g$, we use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}. The HOD models the galaxy content of dark matter haloes as being made up of central and satellite galaxies. Centrals lie at the centre of the halo, while satellites are distributed according to a profile $u_s(r|M)$. Haloes can have zero or one central, and the mean number of centrals for a halo of mass $M$ is modelled as a smoothed step function
      \begin{equation}
        \langle N_c(M)\rangle=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\rm lnM}}\right)\right].
      \end{equation}
      We then assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, the average number of satellites follows a power law of the form:
      \begin{equation}
        \langle N_s(M)\rangle=N_c(M)\,\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
      \end{equation}
      For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$.

>>>>

\title[Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations]{Wide-angle tomographic measurement of the intergalactic gas pressure through galaxy-tSZ Fcross-correlations}
\author[David Alonso]{Nick Koukoufilippas$^1$, David Alonso$^1$, Maciej Bilicki$^2$, John A. Peacock$^3$\\
                      $^{1}$Department of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK\\
                      $^{2}$Center for Theoretical Physics, Polish Academy of Sciences, al. Lotnik\'ow 32/46, 02-668, Warsaw, Poland\\
                      $^{3}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ, United Kingdom
                      }

@@

    \subsubsection{Galaxies and the halo occupation distribution}\label{sssec:theory.hm.hod}
      To model the galaxy overdensity, $\Delta_g$, we use a Halo Occupation Distribution (HOD) model \citep{2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}, as prescribed by \cite{2011ApJ...736...59Z}. The HOD models the galaxy content of dark matter haloes as being made up of central and satellite galaxies. Centrals lie at the centre of the halo, while satellites are distributed according to a profile $u_s(r|M)$. Haloes can have zero or one central, and the mean number of centrals for a halo of mass $M$ is modelled as a smoothed step function
      \begin{equation}
        \langle N_c(M)\rangle=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\rm lnM}}\right)\right].
      \end{equation}
      In our fiducial scenario we assume that satellites can only be formed if a halo has a central and has a mass larger than some threshold $M_0$. In that case, the average number of satellites follows a power law of the form:
      \begin{equation}
        \langle N_s(M)\rangle=N_c(M)\,\Theta(M-M_0)\,\left(\frac{M-M_0}{M_1'}\right)^{\alpha_s}.
      \end{equation}
      For simplicity, we fix $M_0$ to $M_{\rm min}$, $\sigma_{\rm lnM}=0.15$ and $\alpha_s$=1, as in \cite{2018MNRAS.473.4318A}, leaving only two free parameters: $M_{\rm min}$ and $M_1'$.

      Coupling $M_0$ and $M_{\rm min}$ allows for all haloes containing a central to also contain satellites, and conversely, for all haloes containing satellites to necessarily contain a central. This assumption breaks down in cases such as mergers, where centrals have not been established yet. Nevertheless, we have confirmed that decoupling $M_0$ and $M_{\rm min}$, and allowing haloes to contain solely satellites, does not yield any statistically significant offset from our fiducial scenario. We have also tested the effect of freeing-up $\sigma_{\rm lnM}$, and confirmed that the measurements we obtain are almost identical to our fiducial results.
